Output Summary

### 2021-07-27 03-post-process/output-plots-single.Rmd
Create duplicates of key files
These will archive the single-population version and the main version files will be edited to be applicable to multiple populations.

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'MIN' = 'Minam', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: "base"
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---

>>>>

---
title: "Output Summary"
subtitle: "`r c('CAT' = 'Catherine Creek', 'LOS' = 'Lostine', 'MIN' = 'Minam', 'UGR' = 'Upper Grande Ronde')[params$pop]`"
output: 
  html_document:
    toc: true
    toc_float: true
params:
  pop:
    label: "Population"
    value: CAT
    input: select
    choices: [CAT, LOS, UGR]
  scenario:
    label: "Scenario"
    value: "base-single"
    input: text
  mcmc_plots:
    label: "Make MCMC Plots"
    input: checkbox
    value: FALSE
editor_options: 
  chunk_output_type: console
---
